PM Mungbean meta-analysis

### 2020-04-01 02_Preliminary_analysis.Rmd
Correct filepath

lm_rain1 <-
   read.csv("data/lmInSeasonRainfall_-10.09_30.64.csv",
            stringsAsFactors = FALSE)
lm_rain2 <-
   read.csv("data/lmInSeasonRainfall_-10.09_65.100.csv",
            stringsAsFactors = FALSE)
lm_rain3 <-
   read.csv("data/lmInSeasonRainfall_10.30_30.64.csv",
            stringsAsFactors = FALSE)
lm_rain4 <-
   read.csv("data/lmInSeasonRainfall_10.30_65.100.csv",
            stringsAsFactors = FALSE)

>>>>

lm_rain1 <-
   read.csv("cache/lmInSeasonRainfall_-10.09_30.64.csv",
            stringsAsFactors = FALSE)
lm_rain2 <-
   read.csv("cache/lmInSeasonRainfall_-10.09_65.100.csv",
            stringsAsFactors = FALSE)
lm_rain3 <-
   read.csv("cache/lmInSeasonRainfall_10.30_30.64.csv",
            stringsAsFactors = FALSE)
lm_rain4 <-
   read.csv("cache/lmInSeasonRainfall_10.30_65.100.csv",
            stringsAsFactors = FALSE)
